Deciding to Disclose

### 2017-04-08 agent_models.tex
viva version

While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same output - a decision, we limit ourselves here to four. The simplest is a lexicographic rule (1), in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}. Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-output characteristics.

@@

The lexicographic heuristic \citep{Luce1956,Fishburn1974} (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified problem representation, where an action is a choice between combined lotteries. Functionally, the heuristic maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e. one reason decision making. Where there is no clear best action, but one or more is evidently worse, a choice must be made as to whether to discard the poorer action; in this case we have elected to retain it.
This approach requires minimal computation, and does not assume that \(u_{i}\) is static, or known.

@@

Given the discrete nature of actions and payoffs, coupled with a desire for tractability of the
simulation, the Dirichlet distribution is employed as a prior to represent these beliefs. 
The distribution is particularly convenient, in that to infer the
probability of a signal implying a payoff is
simply -

@@

Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), and \(\alpha_{i}\) is the pseudo-count of prior observations\footnote{Psuedo-counts are related to, but distinct from prior beliefs. Here, the pseudo-count is a parameter of the prior Dirichlet distribution and is nothing more than a hypothetical count of prior observations. The outcome is a result of the relationship between $\alpha$, and $n$, which is increasingly driven by the priors as fir higher values of $alpha$.} for a pair \(i\). Hence,
the belief that a signal will lead to a payoff is the number
of times that pairing has been observed (including the pseudo-count),
over the total number of observations thus far. This makes computation
of beliefs fast and simple, since all that must be maintained is
a count of observations.
As before, midwives follow a similar pattern but maintain \(n_{s_{w}}\) independent counts of pairings between referral choice and payoff, updating their beliefs about the relationship between the choice to refer and payoff given the signal they have received.

@@

\begin{equation}
R_{w}(s_{w}, \theta_{w}) = \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, \theta_{w}, j)p(j)p(i | s_{w}),
\end{equation}

@@

\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{m}(s_{w}, s_{m}, i)p(i | s_{w})
\end{equation}

@@

%Maybe cut this bit and make explanation richer?
\ac{CPT} uses transformed probabilities, under weighting small probabilities, and over weighting large ones. This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and in contrast, low probabilities as impossible. The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains (\ref{eqn:cpt_p_pos}) and losses (\ref{eqn:cpt_p_neg}):

@@

\begin{equation}
\pi_{n}^{+}=w^{+}(p_{n})
\end{equation}
\begin{equation}
\pi_{-m}^{-}=w^{-}(p_{-m})
\end{equation}
\begin{equation}
\pi_{i}^{+}=w^{+}(p_{i}+\ldots+p_{n}) - w^{+}(p_{i+1}+\ldots+p_{n}),0\leq i \leq n - 1
\end{equation}
\begin{equation}
\pi_{i}^{-}=w^{-}(p_{-m}+\ldots+p_{i}) - w^{-}(p_{-m}+\ldots+p_{i-1}),1-m\leq i \leq 0
\end{equation}

>>>>

While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same output - a decision, I have limited myself here to four. The simplest is a lexicographic rule (1), in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}. Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-output characteristics.

@@

The lexicographic heuristic \citep{Luce1956,Fishburn1974} (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified problem representation, where an action is a choice between combined lotteries. Functionally, the heuristic maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e. one reason decision making. Where there is no clear best action, but one or more is evidently worse, a choice must be made as to whether to discard the poorer action; in this case I have elected to retain it.
This approach requires minimal computation, and does not assume that \(u_{i}\) is static, or known.

@@

Given the discrete nature of actions and payoffs, coupled with a desire for tractability of the
simulation, the Dirichlet distribution is employed as a prior to represent these beliefs \citep{Agresti2005}. 
The distribution is particularly convenient, in that to infer the
probability of a signal implying a payoff is
simply -

@@

Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), and \(\alpha_{i}\) is the pseudo-count of prior observations\footnote{Psuedo-counts are related to, but distinct from prior beliefs. Here, the pseudo-count is a hyperparameter of the prior Dirichlet distribution and is nothing more than a hypothetical count of prior observations. The outcome is a result of the relationship between $\alpha$, and $n$, which is increasingly driven by the priors as for higher values of $\alpha$.} for a pair \(i\). Hence,
the belief that a signal will lead to a payoff is the number
of times that pairing has been observed (including the pseudo-count),
over the total number of observations thus far. This makes computation
of beliefs fast and simple, since all that must be maintained is
a count of observations.
As before, midwives follow a similar pattern but maintain \(n_{s_{w}}\) independent counts of pairings between referral choice and payoff, updating their beliefs about the relationship between the choice to refer and payoff given the signal they have received.

@@

\begin{equation}
R_{w}(s_{w}, \theta_{w}) = \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, \theta_{w}, j)p(j)p(i | s_{w})\label{eq:w_brm},
\end{equation}

@@

\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{m}(s_{w}, s_{m}, i)p(i | s_{w})\label{eq:mw_brm}
\end{equation}

@@

%Maybe cut this bit and make explanation richer?
\ac{CPT} uses transformed probabilities, under weighting small probabilities, and over weighting large ones. This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and in contrast, low probabilities as impossible. The correct weighting function is subject to some debate, but here I have used that of \citet{Tversky1992}, which treats probabilities differently for gains (\ref{eqn:cpt_p_pos}) and losses (\ref{eqn:cpt_p_neg}):

@@

\begin{equation}
\pi_{n}^{+}=w^{+}(p_{n})
\end{equation}
\begin{equation}
\pi_{-m}^{-}=w^{-}(p_{-m})
\end{equation}
\begin{equation}
\pi_{i}^{+}=w^{+}(p_{i}+\ldots+p_{n}) - w^{+}(p_{i+1}+\ldots+p_{n}),0\leq i \leq n - 1
\end{equation}
\begin{equation}
\pi_{i}^{-}=w^{-}(p_{-m}+\ldots+p_{i}) - w^{-}(p_{-m}+\ldots+p_{i-1}),1-m\leq i \leq 0\label{eq:cpt_end}
\end{equation}

### 2017-04-08 motivation.tex
Cleaning up
viva version

\section{Methods and Motivation}
\label{sec:model_design}

The appropriate game representative of the scenario of interest, which captures the desired strategic dynamics may not be immediately obvious. There will almost invariably be many possible alternatives, of which some are isomorphisms, and others fundamentally different conjectures about the data generating process. We suggest that an iterative process is beneficial, beginning from the simplest possible game, and progressively augmenting it.

Transitioning from the resulting game, to a set of decision problems is a relatively simple task. We treat the $n$ player game as $n$ one-player games \citep{RiosInsua2009}, where the moves of other players are drawn from a probability distribution - nature, in game theoretic parlance. As with the game, the decision problem representation admits a degree of variation, and may need to be adjusted to reflect the decision rules that will be used.

>>>>

\section{Approach and Motivation}
\label{sec:model_design}

The appropriate game representative of the scenario of interest, which captures the desired strategic dynamics may not be immediately obvious. There will almost invariably be many possible alternatives, of which some are isomorphisms, and others fundamentally different conjectures about the data generating process. I would suggest that an iterative process is beneficial, beginning from the simplest possible game, and progressively augmenting it.

Transitioning from the resulting game, to a set of decision problems is a relatively simple task. I have treated the $n$ player game as $n$ one-player games \citep{RiosInsua2009}, where the moves of other players are drawn from a probability distribution - nature, in game theoretic parlance. As with the game, the decision problem representation admits a degree of variation, and may need to be adjusted to reflect the decision rules that will be used.
